### 2024-04-30 about/vita.tex
eca
Ahoy

\leftright{\bf Ph.D.\ Mathematics}{\bf September 2023 -- present}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Supervisors: Andrew Granville and Hamed Hatami.
\medbreak
\leftright{\bf M.Sc.\ Mathematics}{\bf May 2021 -- present}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Supervisor: Luc Devroye. CGPA: 4.00/4.
Thesis: Structural properties of conditional Galton--Watson trees.
\medbreak
\leftright{\bf B.Sc.\ Joint Honours Mathematics and Computer Science}{\bf September 2017 -- April 2021}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Minor: Linguistics. CGPA: 3.84/4.
\medbreak
\leftright{\bf Exchange semester}{\bf February -- June 2019}
\leftright{\sl Faculty of Mathematics and Physics, Charles University}{\sl Prague, Czech Republic}
\smallskip
Grade: 1 on all courses (highest score attainable).

@@

\begingroup\frenchspacing
\papercount=6
\pubbegin P
\papitem (with Jonah Saks)
On the homology of several number-theoretic set families. To appear in
{\sl Enumerative Combinatorics and Applications} (2024), 17~pp.
[arXiv:2206.12535]
\papitem (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions.
{\sl Australasian Journal of Combinatorics}\/ {\bf 84},3 (2022), 357--374.
[arXiv:2106.05949]
\papitem (with Luc Devroye and Rosie Y. Zhao)
On the peel number and the leaf-height of a Galton--Watson tree.
{\sl Combinatorics, Probability and Computing}\/ {\bf 32},1 (2023), 68--90.
[arXiv:2106.14389]
\papitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl Discrete Mathematics
and Theoretical Computer Science}\/ {\bf 24},1 (2022), \#7, 16~pp.
[arXiv:2105.12046]
\papitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. {\sl Random Structures and Algorithms}\/ {\bf 61},3 (2022), 520--542.
[arXiv:2007.05681]
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set.
{\sl Integers: Electronic Journal of Combinatorial Number Theory}\/ {\bf 21} (2021), \#A89, 19~pp.
[arXiv:2012.12339]

\goodbreak
\sectheader{Reports}

@@

\sectheader{Published Short Fiction}

@@

\starleftright{\bf Teaching assistant}{\bf September 2021 -- present}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Teaching assistant in the following courses. Duties include giving tutorials, holding office hours, and
grading assignments and exams.
\begingroup\parindent=10pt
\smallskip
\thing Fall 2023: MATH 240 Discrete Structures
\smallskip
\thing Fall 2021: COMP 690 Probabilistic Analysis of Algorithms
\endgroup
\medbreak

@@

\leftright{\bf DRP Mentor}{\bf January -- April 2022}
\leftright{\sl Department of Mathematics and Statistics, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Met with two undergraduate students as part of the Directed Reading Program
on a weekly basis to give them an introduction to research-level
mathematics in a casual setting. Focused on topics in extremal combinatorics related to the increasing
triples problem, as well as topics related to Khovanskii's theorem.
\medbreak

>>>>

\leftright{\bf Ph.D.\ Mathematics}{\bf September 2023 -- present}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Supervisor: Hamed Hatami.
\medbreak
\leftright{\bf M.Sc.\ Mathematics}{\bf May 2021 -- August 2022}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Supervisor: Luc Devroye. CGPA: 4.00/4.
Thesis: Structural properties of conditional Galton--Watson trees.
\medbreak
\leftright{\bf B.Sc.\ Joint Honours Mathematics and Computer Science}{\bf September 2017 -- April 2021}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Minor: Linguistics. CGPA: 3.84/4.
\medbreak
\leftright{\bf Exchange semester}{\bf February -- June 2019}
\leftright{\sl Faculty of Mathematics and Physics, Charles University}{\sl Prague, Czech Republic}
\smallskip
Grade: 1 on all courses (highest score attainable).

@@

\begingroup\frenchspacing
\papercount=6
\pubbegin P
\papitem (with Jonah Saks)
On the homology of several number-theoretic set families.
{\sl Enumerative Combinatorics and Applications}\/ {4},2 (2024), \#S2R12, 11~pp.
[arXiv:2206.12535]
\papitem (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions.
{\sl Australasian Journal of Combinatorics}\/ {\bf 84},3 (2022), 357--374.
[arXiv:2106.05949]
\papitem (with Luc Devroye and Rosie Y. Zhao)
On the peel number and the leaf-height of a Galton--Watson tree.
{\sl Combinatorics, Probability and Computing}\/ {\bf 32},1 (2023), 68--90.
[arXiv:2106.14389]
\papitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl Discrete Mathematics
and Theoretical Computer Science}\/ {\bf 24},1 (2022), \#7, 16~pp.
[arXiv:2105.12046]
\papitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. {\sl Random Structures and Algorithms}\/ {\bf 61},3 (2022), 520--542.
[arXiv:2007.05681]
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set.
{\sl Integers: Electronic Journal of Combinatorial Number Theory}\/ {\bf 21} (2021), \#A89, 19~pp.
[arXiv:2012.12339]

\goodbreak
\sectheader{Reports and Theses}

@@

\sectheader{Published Fiction}

@@

\leftright{\bf Co-Editor}{\bf December 2023 -- present}
\leftright{\sl Ahoy Literary Magazine}{\sl Montr\'eal, QC, Canada}
\smallskip
Founding co-editor of a semiannual print magazine that publishes poetry, prose, and art.
In charge of English short fiction submissions and the overall typesetting. Share duties with the other
co-editors related to marketing, emails, and sales.
\medbreak

\starleftright{\bf Teaching assistant}{\bf September 2021 -- present}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Teaching assistant in the following courses. Duties include giving tutorials, holding office hours, and
grading assignments and exams.
\begingroup\parindent=10pt
\smallskip
\thing Winter 2024, Fall 2023: MATH 240 Discrete Structures
\smallskip
\thing Fall 2021: COMP 690 Probabilistic Analysis of Algorithms
\endgroup
\medbreak

\leftright{\bf DRP Mentor}{\bf January 2022 -- April 2024}
\leftright{\sl Department of Mathematics and Statistics, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Met with two undergraduate students as part of the Directed Reading Program
on a weekly basis to give them an introduction to research-level
mathematics in a casual setting. Focused on topics in extremal combinatorics related to the increasing
triples problem, as well as topics related to Khovanskii's theorem.
\medbreak

@@
